### 2023-08-24 paper/sec-results.tex
pap

As discussed in Sect.~\ref{subsec:pdf_impact_assessment}, the PDF sensitivity
studies of the FPF neutrino data based on the {\sc\small xFitter} profiling
of PDF4LHC21 are complemented by those based on their direct inclusion
in the NNPDF4.0 global analysis.
%
Here we present results for the impact of the combined FPF neutrino
measurements on NNPDF4.0, namely the analogous study of that shown
in Fig.~\ref{fig:FPF_combined} for PDF4LHC21.
%
While we have produced results also the variations studied in
Sect.~\ref{sec:pdf4lhc21} with the NNPDF fitting methodology, the qualitative
findings are compatible with those obtained with {\sc\small xFitter} and
hence it is not necessary to duplicate them here.

Fig.~\ref{fig:NNPDF40_baseline} displays the
same results as Fig.~\ref{fig:FPF_combined} now in the case of the
fits obtained with the NNPDF4.0 fitting methodology.
%
The baseline NNPDF4.0 NNLO analysis is compared
with the results of the fits which include the combined FPF dataset,
in both the statistics-only scenario and for the case
where systematic uncertainties are also accounted for.
%
As in the PDF4LHC21 analysis, the bands indicate the one-sigma PDF uncertainties.
%
Note that we also show results for the charm PDF (bottom right panel), which
in the NNPDF4.0 fit is also determined directly from the data entering
the fit~\cite{Ball:2016neh}.
%
In this way we can determine the possible constraints that neutrino
DIS measurements at the LHC may impose on the intrinsic charm
content of the proton~\cite{Ball:2022qks}.

@@

From  Fig.~\ref{fig:NNPDF40_baseline} one finds that
the impact on the PDFs found by direct inclusion of the FPF structure
functions on the NNPDF4.0 fit is qualitatively consistent with
that found from the Hessian profiling of PDF4LHC21.

>>>>

As discussed in Sect.~\ref{subsec:pdf_impact_assessment}, the PDF sensitivity
studies of the FPF neutrino data based on the {\sc\small xFitter} profiling
of PDF4LHC21 are complemented by those based on their direct inclusion
in the NNPDF4.0 global analysis.
%
Here we present results for the impact of the combined FPF neutrino
measurements on NNPDF4.0, namely the analogous study of that shown
in Fig.~\ref{fig:FPF_combined} in the case of PDF4LHC21.
%
We emphasize that we have produced results for the variations studied in
Sect.~\ref{sec:pdf4lhc21} also with the NNPDF fitting methodology.
%
Given that the qualitative obtained with the NNPDF fits
are compatible with those obtained with {\sc\small xFitter}, it is not necessary to duplicate them here,
and hence we only show results for the impact of the combined FPF pseudo-data.

Fig.~\ref{fig:NNPDF40_baseline} displays the
same results as Fig.~\ref{fig:FPF_combined} now in the case of the
fits obtained with the NNPDF4.0 fitting methodology.
%
The baseline NNPDF4.0 NNLO analysis is compared
with the results of the fits which include the combined FPF dataset,
in both the statistics-only scenario and for the case
where systematic uncertainties are also accounted for.
%
As in the PDF4LHC21 analysis, the bands indicate the one-sigma PDF uncertainties.
%
Note that we also show results for the charm PDF (bottom right panel), which
in the NNPDF4.0 fit is also determined directly from the data entering
the fit~\cite{Ball:2016neh}.
%
In this way, we can determine the possible constraints that neutrino
DIS measurements at the LHC may impose on the intrinsic charm
content of the proton~\cite{Ball:2022qks}.

@@

From  Fig.~\ref{fig:NNPDF40_baseline} one finds that
the impact on the PDFs found by direct inclusion of the FPF structure
functions on the NNPDF4.0 fit is qualitatively consistent with
that found in the the Hessian profiling of PDF4LHC21.
%
In particular, the constraints are more significant for the up and down
quark valence PDFs as well as for the total strangeness.
%
As was the case with the PDF4LHC21 baseline, the uncertainty reduction
in the case of the strangeness PDF is particularly
striking.
%
Also consistently with Sect.~\ref{sec:pdf4lhc21}, the gluon
PDF is unchanged, and the impact on the total quark PDF
is restricted to the large-$x$ region.
%
While one can also identify differences related to analysis choices
such as the PDF parametrisation and the method used to assess the PDF
error reduction (for example for the small-$x$ behaviour of $xu_V$ and $xd_V$)
we conclude that by and large the projected impact of the FPF structure function
measurements us robust against the specific fitting methodology adopted.
